---
title: "PinkTutorial"
author: "Jules Hanhart"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install Instructions:
enter the following code into your console of rstudio. 
```{r}
devtools::install_github("juleshanhart/1hanhart.pkg")
```

```{r}
library(tidyverse)
library(dplyr)
library(broom)
library(knitr)
library(ggplot2)
```

Data being used: surveys dataset
Download Data Instructions: 
enter the following code into your console of rstudio.
```{r}
read_csv("/cloud/project/hanhart.pkg/data/surveys.csv")
```

This package will consolidate and condense data, making it easier to look at, and then turn the final plot pink so I like it more.


Function 1: a function to clean data- consolidate function
The consolidate function removes NA values and simultaneously deletes the majority of columns in order to return four "focus" columns. 
example: 
```{r}
consolidate <- function(data){
    clean <- data %>% 
        na.omit(data) %>% 
        select(weight, hindfoot_length, sex, species_id) %>% 
        return(clean)
}
#head(consolidate(surveys))
```

Function 2: a function to manipulate data- mutate function
The mutate function converts the data in the weight column from grams to pounds. 
example: 
```{r}
weight_in_lbs <- function(data = surveys){
  clean <- data %>% 
  mutate(weight_in_lbs = weight*0.0022) %>% 
  return(clean)
}
#head(weight_in_lbs(surveys))
```

Function 3: a statistical function- lm function
The lm function fits a linear model using plot_id and weight, giving information about residuals, error rates, estimates, etc.
example: 
```{r}
linearmodel <- function(data){
   clean <- data %>% 
       lm(formula = plot_id~weight, data = surveys) %>% 
   return(clean)
}
#summary(linearmodel(unlist(data)))
```

Function 4: a function that plots data - point plot function
The point plot function returns a plot using geom_point(), of weight and species_id grouped by sex. 
example: 
```{r}
pointplot <- function(x = weight, y = species_id, surveys){
    ggplot(data = surveys, mapping = aes(x = weight, y = species_id, col = sex)) + geom_point()
}
#pointplot('weight', 'species_id', surveys)
```

Function 5: a function for fun- pink function
The pink function simply turns the colors in the previous graph pink so that I enjoy looking at it more. 
example: 
```{r}
pinkfunction <- function(x = weight, y = species_id,surveys){
  ggplot(data = surveys, mapping = aes(x = weight, y = species_id, col = sex)) + geom_point() + stat_smooth(method = lm, col = "hotpink") + theme(text = element_text(color =  "pink"))
}
#pinkfunction('weight', 'species_id', surveys)
```
